\documentclass[]{article}
\usepackage[margin=1in,headheight=28pt]{geometry}
\overfullrule=2cm
\newcommand{\datefillin}{\hspace{0.2cm}\rule{3cm}{.1pt}}
\newcommand{\tabmed}[1]{\makebox[.22\linewidth][l]{#1}\ignorespaces}
\newcommand{\tablarge}[1]{\makebox[.55\linewidth][l]{#1}\ignorespaces}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\LARGE Caregiver Manager Memorandum}
\cfoot{}
\enlargethispage{40pt}
\begin{document}
\begin{enumerate}
	\item \textbf{Parties}. This Agreement is between \vspace{.25cm}\\
		\tabmed{Joan B Harrison} Owner of residential real property at\\ 
		\tabmed{}104 N Wilson, \#13\\
		\tabmed{}Pasadena, CA 91106 \vspace{.25cm}\\
		and \vspace{.25cm}\\
		\tabmed{Colin Keenan} \tabmed{home address:} 3835 Park Ave, Kansas City, MO 64109\\
		\tabmed{}\tabmed{phone number:} 816-200-2658\\ 
		\tabmed{}\tabmed{email address:} colinnkeenan@gmail.com\\
		Manager of caregivers.\vspace{.25cm}
	\item \textbf{Beginning Date}. Manager will begin work on 5/18/2015.
	\item \textbf{Responsibilities}. Manager's duties are set forth below:
		\begin{enumerate}
			\item \textbf{Hiring Caregivers}
				\begin{enumerate}
					\item advertise positions
					\item answer phone inquiries about positions
					\item interview applicants
					\item accept employment applications
					\item conduct background and drug tests
					\item select caregivers
				\end{enumerate}
			\item \textbf{Training and Oversight}
				\begin{enumerate}
					\item supervise caregivers hired by Joan Harrison under a senior care contract
					\item provide at least 10 hours of training to each new hire
					\item communicate with caregivers daily when they call to check in or check out
					\item review and discuss blood sugar readings with caregivers and doctor
					\item discuss other health issues as appropriate
					\item keep caregivers informed about changes in medication verbally and by email
					\item monitor appointments, making sure not more than two per week and that caregiver has arranged transportation for each appointment
					\item call Joan at critical times to have her check her own blood sugar and take action if needed
					\item if a camera feed has been established, monitor the feed regularly throughout the day to notice any potential issues
				\end{enumerate}
			\item \textbf{Payroll}. implement the payroll procedures set forth in the Senior Care Contract.
			\item \textbf{Other Duties}. any other duties as set forth under the Senior Care Contract.
		\end{enumerate}
	\item \textbf{Availability}. Manager will be available by telephone and email 24 hours a day, 7 days a week.
	\item \textbf{Payment Terms}. Manager will be paid \$0.
	\item \textbf{Ending the Manager's Employment}. Owner may terminate Manager's employment at any time, for any reason that is not unlawful, with or without notice. Manager may quit at any time, for any reason, with or without notice.
	\item \textbf{Amendments}. All agreements between Owner and Manager relating to the work specified in this Agreement are incorporated in this Agreement. Any modification to the Agreement must be in writing and signed by both parties.
	\item \textbf{Place of Execution}. Signed at Pasadena, California
\end{enumerate}

\vspace{.5cm}
\noindent\tabmed{Manager Signature} \tablarge{\makebox[.5\linewidth]{\hrulefill}} \tabmed{Date\datefillin} \\*
\tabmed{} \tablarge{\textsuperscript{Colin Keenan}}

\vspace{.5cm}
\noindent\tabmed{Owner Signature} \tablarge{\makebox[.5\linewidth]{\hrulefill}} \tabmed{Date\datefillin} \\*
\tabmed{} \tablarge{\textsuperscript{Joan B Harrison}} 
\end{document}
