\documentclass[]{article}
\usepackage[margin=1in,headheight=28pt]{geometry}
\overfullrule=2cm
\newcommand{\datefillin}{\hspace{0.2cm}\rule{3cm}{.1pt}}
\newcommand{\tabmed}[1]{\makebox[.22\linewidth][l]{#1}\ignorespaces}
\newcommand{\tablarge}[1]{\makebox[.55\linewidth][l]{#1}\ignorespaces}
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{\LARGE Residential Rental Property Manager Memorandum}
\cfoot{}
\enlargethispage{40pt}
\begin{document}
\begin{enumerate}
	\item \textbf{Parties}. This Agreement is between \vspace{.25cm}\\
		\tabmed{Joan B Harrison} Owner of residential real property at\\ 
		\tabmed{}104 N Wilson, \#13\\
		\tabmed{}Pasadena, CA 91106 \vspace{.25cm}\\
		and \vspace{.25cm}\\
		\tabmed{Colin Keenan} \tabmed{home address:} 3835 Park Ave, Kansas City, MO 64109\\
		\tabmed{}\tabmed{phone number:} 816-200-2658\\ 
		\tabmed{}\tabmed{email address:} colinnkeenan@gmail.com\\
		Manager of the property.\vspace{.25cm}
	\item \textbf{Beginning Date}. Manager will begin work on 5/11/2015.
	\item \textbf{Responsibilities}. Manager's duties are set forth below:
		\begin{enumerate}
			\item \textbf{Renting Room}
				\begin{enumerate}
					\item advertise vacant room
					\item answer phone inquiries about vacant room
					\item show vacant room
					\item accept rental applications
					\item select lodger
				\end{enumerate}
			\item \textbf{Rent Collection}
				\begin{enumerate}
					\item oversee rent payments made by lodger
					\item provide email rent receipts
					\item maintain rent collection records
					\item prepare late rent notices (pay or quit)
					\item serve late rent notices on lodger
					\item serve rent increase and tenancy termination notices
				\end{enumerate}
			\item \textbf{Repairs}
				\begin{enumerate}
					\item accept lodger complaints and repair requests
					\item maintain written log of lodger complaints
					\item hire outside help as needed to complete maintenance and repairs
				\end{enumerate}
			\item \textbf{Other Duties}. any other duties as set forth under the Wilson Manor, Bedroom in Condominium Apartment 13, Week-to-Week Lodging Rental Agreement.
			\item \textbf{Other Managers of the Property}. oversee and contact other property managers authorized by Owner to carry out on-site duties such as overseeing outside help and posting notices.
		\end{enumerate}
	\item \textbf{Availability}. Manager will be available by telephone and email 24 hours a day, 7 days a week.
	\item \textbf{Payment Terms}. Manager will be paid \$0.
	\item \textbf{Ending the Manager's Employment}. Owner may terminate Manager's employment at any time, for any reason that is not unlawful, with or without notice. Manager may quit at any time, for any reason, with or without notice.
	\item \textbf{Amendments}. All agreements between Owner and Manager relating to the work specified in this Agreement are incorporated in this Agreement. Any modification to the Agreement must be in writing and signed by both parties.
	\item \textbf{Place of Execution}. Signed at Pasadena, California
\end{enumerate}

\vspace{.5cm}
\noindent\tabmed{Manager Signature} \tablarge{\makebox[.5\linewidth]{\hrulefill}} \tabmed{Date\datefillin} \\*
\tabmed{} \tablarge{\textsuperscript{Colin Keenan}}

\vspace{.5cm}
\noindent\tabmed{Owner Signature} \tablarge{\makebox[.5\linewidth]{\hrulefill}} \tabmed{Date\datefillin} \\*
\tabmed{} \tablarge{\textsuperscript{Joan B Harrison}} 
\end{document}
