\documentclass[]{article}
\overfullrule=2cm
\usepackage[margin=1in,headheight=28pt]{geometry}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{0}

\date{}

\begin{document}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\item
  \begin{quote}
  Nolo Legal Agreements
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    California Residential Lease: Though basic, looks good for our needs
    \end{quote}
  \item
    \begin{quote}
    Elder Care Agreement: Very basic employee contract for home health
    caregiver. Given the novel way in which we are constructing our
    contract, may be a challenge to use it.
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  \href{http://care.com}{\emph{Care.com}}
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    Sample Adult and Senior Care Contract: Looks way more promising.
    Clearly lists all of the tasks. Does not provide specific provisions
    for fringe benefits such as food and lodging however. \\*
    \href{http://cdn-care.com/media/cms/pdf/adult-and-senior-care-contract-caredotcom.pdf}{\emph{http://cdn-care.com/media/cms/pdf/adult-and-senior-care-contract-caredotcom.pdf}}
    \end{quote}
  \item
    \begin{quote}
    Adult and Senior Care Rules: These rules supplement the contract.\\*
    \href{https://www.care.com/a/adult-and-senior-care-rules-to-discuss-before-you-hire-1408721025155}{\emph{https://www.care.com/a/adult-and-senior-care-rules-to-discuss-before-you-hire-1408721025155}}
    \end{quote}
  \item
    \begin{quote}
    Daily Schedule: supplements the contract.\\*
    \href{https://www.care.com/a/daily-schedule-for-adult-and-senior-caregivers-1408720203114}{\emph{https://www.care.com/a/daily-schedule-for-adult-and-senior-caregivers-1408720203114}}
    \end{quote}
  \item
    \begin{quote}
    Payroll Services: Homepay by Breed
    \end{quote}

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \item
      \begin{quote}
      Comprehensive Service: Covers handling all payroll and tax
      obligations associated with household employment. This includes
      processing your employee's payroll, tracking your tax liability,
      filing state and federal tax returns on your behalf, remitting
      taxes to the appropriate tax agencies, and unlimited support from
      our team of household payroll and tax experts. \\*
      \href{http://www.myhomepay.com/WelcomeCareMembers}{\emph{http://www.myhomepay.com/WelcomeCareMembers}}
      \end{quote}
    \item
      \begin{quote}
      Fees: Somewhat expensive at \$65 per month, but may be worth it to
      avoid the hassles of tracking everything and to receive unlimited
      support from the household payroll and tax experts.
      \end{quote}

      \begin{enumerate}
      \def\labelenumiv{\alph{enumiv}.}
      \item
        \begin{quote}
        \textbf{Comprehensive Service Fee:} \$195 per quarter..
        \end{quote}
      \item
        \begin{quote}
        \textbf{Direct Deposit Option}+ \$25 per quarter. This optional
        fee covers the electronic funds transfers we'll initiate to pay
        your employee via Direct Deposit -- eliminating check-writing
        for you and trips to the bank for your employee.
        \end{quote}
      \item
        \begin{quote}
        \textbf{Year-End Tax Packet} \$95 Includes preparing all your
        year-end tax documents: Form W-2, Form W-3, Schedule H, State
        Annual Reconciliation (where applicable)
        \end{quote}
      \item
        \begin{quote}
        \textbf{One-Time Setup} \$100 This one-time fee covers setting
        up your account, obtaining your tax IDs and filing your New Hire
        Report.
        \end{quote}
      \end{enumerate}
    \item
      \begin{quote}
      Nanny Tax advice: 888-273-3356
      \end{quote}
    \end{enumerate}
  \end{enumerate}
\item
  \begin{quote}
  Other employment agreements
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    Standard at-will employee contract. \\*
    \href{http://images.inc.com/tools/downloads/21528.doc}{\emph{http://images.inc.com/tools/downloads/21528.doc}}
    \end{quote}
  \item
    \begin{quote}
    U.S. Legal Forms. Employment hiring package. Provides standard
    california employment contracts. \\*
    \href{http://www.uslegalforms.com/ca/CA-P025-PKG.htm}{\emph{http://www.uslegalforms.com/ca/CA-P025-PKG.htm}}
    \end{quote}

    Employment Application
    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \item
      \begin{quote}
      Consent to Drug Testing
      \end{quote}
    \item
      \begin{quote}
      HIPAA Notice of Privacy Practices
      \end{quote}
    \item
      \begin{quote}
      Model Statement of ERISA rights
      \end{quote}
    \item
      \begin{quote}
      Employee Time Sheet
      \end{quote}
    \item
      \begin{quote}
      Direct Deposit Authorization
      \end{quote}
    \item
      \begin{quote}
      Employment Agreement
      \end{quote}
    \item
      \begin{quote}
      Confidentiality Agreement
      \end{quote}
    \item
      \begin{quote}
      Employee Non-compete Agreement
      \end{quote}
    \item
      \begin{quote}
      Employee Nondisclosure Agreement
      \end{quote}
    \item
      \begin{quote}
      Criminal History Check Consent Form
      \end{quote}
    \end{enumerate}
  \item
    \begin{quote}
    \href{http://elderlawanswers.com}{\emph{Elderlawanswers.com}}:
    provides guidance for employee contracts: \\*
    \href{http://www.elderlawanswers.com/care-giving-contracts-5716}{\emph{http://www.elderlawanswers.com/care-giving-contracts-5716}}
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  In Home Help Guidance
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    Family Caregiver Alliance:
    \end{quote}

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \item
      \begin{quote}
      Gives guidelines for placing ads, interviewing, and hiring help. \\*
      \href{https://caregiver.org/hiring-home-help}{\emph{https://caregiver.org/hiring-home-help}}
      \end{quote}
    \item
      \begin{quote}
      Home caregiver contract guidance: \\*
      \href{https://caregiver.org/personal-care-agreements}{\emph{https://caregiver.org/personal-care-agreements}}
      \end{quote}
    \end{enumerate}
  \end{enumerate}
\item
  \begin{quote}
  California law guidance
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    2015 Household Employer's Guide. Send to Colin for his reference. \\*
    \href{http://www.edd.ca.gov/pdf_pub_ctr/de8829.pdf}{\emph{http://www.edd.ca.gov/pdf\_pub\_ctr/de8829.pdf}}
    \end{quote}
  \item
    \begin{quote}
    It appears that the State provides free online, payroll services
    \end{quote}
  \end{enumerate}
\item
  \begin{quote}
  Legal Issues
  \end{quote}

  \begin{enumerate}
  \def\labelenumii{\Alph{enumii}.}
  \item
    \begin{quote}
    Employee Manual Disclaimers. We need to include this on the
    employees manual, the senior care contract and any other written set
    of employee rules to ensure that we don't accidentally create a
    contract. See, \\*
    \href{http://www.americanbar.org/content/newsletter/publications/law_trends_news_practice_area_e_newsletter_home/0705_litigation_employmentcontracts.html}{\emph{http://www.americanbar.org/content/newsletter/publications/law\_trends\_news\_practice\\*\_area\_e\_newsletter\_home/0705\_litigation\_employmentcontracts.html}}
    for guidance
    \end{quote}

    \begin{enumerate}
    \def\labelenumiii{\arabic{enumiii}.}
    \item
      \begin{quote}
      JUST SAY NO? WHEN WON'T DISCLAIMERS WORK? •~ The point of an
      effective disclaimer is to notify employees that the handbook
      statements do not constitute binding promises or enforceable
      commitments. An effective disclaimer undermines contract
      formation. An effective disclaimer clearly proclaims: "We make no
      promises. This is not a contract. You may quit or be terminated at
      any time with or without notice. Nobody has the authority to
      modify this disclaimer." A clear disclaimer is one that a
      reasonable employee will understand, and the understanding will be
      that the employer has not made a commitment to employee job
      security.
      \end{quote}
    \item
      \begin{quote}
      Most employers rely on disclaimers to prevent promises in
      employment handbooks from becoming enforceable contracts:
      \end{quote}

      \begin{enumerate}
      \def\labelenumiv{\alph{enumiv}.}
      \item
        \begin{quote}
        Employers who wish to issue handbooks that do not give rise to
        contractual obligations should use language in the handbook that
        is not language of promise-\/-that is language of discretion or
        guideline, but not language that is mandatory. These employers
        are further urged to use clear and conspicuous disclaimers that
        are attached to every policy to which they apply. A record of
        the employee's understanding of the disclaimer is advised;
        \end{quote}
      \item
        \begin{quote}
        If the employment handbook has already attained contractual
        status, will a subsequent disclaimer do any good? Probably not.
        Subsequent disclaimers are usually analyzed based on contract
        modification rules, and these are usually restrictive.
        \end{quote}
      \end{enumerate}
    \item
      \begin{quote}
      At-will disclaimer. Most employers wish to reserve the right to
      terminate employees at will, or without cause, to insulate
      themselves from lawsuits by former employees claiming that their
      termination was without good cause. An employer should therefore
      state in a disclaimer that while all other policies in the
      handbook can be modified by the employer at any time without a
      written revision of the handbook, the at-will policy cannot be so
      modified. Courts will generally be receptive to employee arguments
      that they are not bound by changes to a policy if they did not
      receive any notice of the change, however, so employers should
      provide timely notice of any new or modified policies.
      \end{quote}
    \end{enumerate}
  \end{enumerate}
\end{enumerate}

\end{document}
